A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-08-01 ms.tex
Update on Overleaf.

We evaluate the hypothesis that the cluster formed in the Leading Arm.  The mean proper motion values in the Magellanic Stream coordinate system \citep{Nidever:2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.  The simulations of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric distances (NEED TO DOUBLE-CHECK THIS).  In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the position of the position of the cluster with a velocity of \vlsr=70 \kmse.

>>>>

% We evaluate the hypothesis that the cluster formed in the Leading Arm.  The mean proper motion values in the Magellanic Stream coordinate system \citep{Nidever:2008} are ($\mu_{\rm MSL}$,$\mu_{\rm MSB}$)=($+$1.X,0.X) mas yr$^{-1}$ which is very similar to the mean values of the LMC and SMC with ($+$1.X,0.X) mas yr$^{-1}$ and ($+$1.X,0.X) mas yr$^{-1}$, respectively.  The simulations of \citet{Besla:2012} also predict proper motions at this position of approximately ($+$1.X,0.X) mas yr$^{-1}$.  The Magellanic Stream simulations give distances of the Leading Arm at this position of $\sim$50 kpc, however, many of these do not include the effects of ram pressure from the hot MW halo which could cause the gas to drop in its orbit to smaller Galactocentric distances (NEED TO DOUBLE-CHECK THIS).  In addition Figure \ref{fig_gass} shows that there is Leading Arm \hi~gas at the position of the position of the cluster with a velocity of \vlsr=70 \kmse.
